Open Data, Open Source and Open Standards in chemistry - The Blue Obelisk five years on

### 2011-04-20 paper.tex
added mentioning of Brunn as per Egon's suggestion
It goes into the Bioclipse paragraph which also got changed a little...

\author{Charles A Darwin\correspondingauthor$^{1,2}$%
       \email{Charles A Darwin\correspondingauthor - charles@londonzoo.co.uk}%
      \and 
         Egon L Willighagen$^3$%
         \email{Egon L Willighagen - egon.willighagen@ki.se}
     \and 
         Rajarshi Guha$^4$%
         \email{Rajarshi Guha - guhar@mail.nih.gov}
	 \and 
	     Christoph Steinbeck$^6$%
	         \email{Christoph Steinbeck - steinbeck@ebi.ac.uk}
     \and 
         Noel M O'Boyle$^5$%
         \email{Noel M O'Boyle - n.oboyle@ucc.ie}
     \and 
         Ola Spjuth$^9$%
         \email{Noel M O'Boyle - n.oboyle@ucc.ie}
     \and 
         Peter Murray-Rust$^7$%
         \email{Peter Murray-Rust - pm286@cam.ac.uk}
     \and
         Robert Hanson$^8$%
         \email{Robert Hanson - hansonr@stolaf.edu}
      \and
         Jane E Doe\correspondingauthor$^2$%
         \email{Jane E Doe\correspondingauthor - jane.e.doe@cambridge.co.uk}
      \and
         Dmitry Pavlov$^8$%
         \email{Dmitry Pavlov - dpavlov@ggasoftware.com}
      }

@@

Bioclipse~\cite{Spjuth:2007fk} (v2.4 released in Aug 2010) and Avogadro
\cite{WebAvogadro} (v1.0 in Oct 2009) are two examples of such
software, based on the CDK and Open Babel, respectively. Bioclipse is
an award-winning `molecular workbench' for life sciences with a dynamic plugin architectur, and which wraps cheminformatics functionality behind user-friendly interfaces and graphical editors. All functionality in Bioclipse is completely scriptable using an integrated high-level language called Bioclipse Scripting Language (BSL), which can be used for invoking functionality or to automate complex tasks~\cite{Bioclipse2}.

Avogadro is a 3D molecular editor and viewer aimed at preparing
and analysing computational chemistry calculations. An interesting
aspect of both of these projects is that they share some developers
with the underlying toolkit and this has driven the development of new
features in the CDK and Open Babel.

>>>>

\author{Charles A Darwin\correspondingauthor$^{1,2}$%
       \email{Charles A Darwin\correspondingauthor - charles@londonzoo.co.uk}%
      \and 
         Egon L Willighagen$^3$%
         \email{Egon L Willighagen - egon.willighagen@ki.se}
     \and 
         Rajarshi Guha$^4$%
         \email{Rajarshi Guha - guhar@mail.nih.gov}
	 \and 
	     Christoph Steinbeck$^6$%
	         \email{Christoph Steinbeck - steinbeck@ebi.ac.uk}
     \and 
         Noel M O'Boyle$^5$%
         \email{Noel M O'Boyle - n.oboyle@ucc.ie}
     \and 
         Ola Spjuth$^9$%
         \email{Noel M O'Boyle - n.oboyle@ucc.ie}
     \and 
         Jonathan Alvarsson$^9$%
         \email{Jonathan Alvarsson - jonathan.alvarsson@farmbio.uu.se}
     \and 
         Peter Murray-Rust$^7$%
         \email{Peter Murray-Rust - pm286@cam.ac.uk}
     \and
         Robert Hanson$^8$%
         \email{Robert Hanson - hansonr@stolaf.edu}
      \and
         Jane E Doe\correspondingauthor$^2$%
         \email{Jane E Doe\correspondingauthor - jane.e.doe@cambridge.co.uk}
      \and
         Dmitry Pavlov$^8$%
         \email{Dmitry Pavlov - dpavlov@ggasoftware.com}
      }

@@

Bioclipse~\cite{Spjuth:2007fk} (v2.4 released in Aug 2010) and Avogadro
\cite{WebAvogadro} (v1.0 in Oct 2009) are two examples of such software, based
on the CDK and Open Babel, respectively. Bioclipse is an award-winning
`molecular workbench' for life sciences with a dynamic plugin architecture, and
which wraps cheminformatics functionality behind user-friendly interfaces and
graphical editors. All functionality in Bioclipse is completely scriptable
using an integrated high-level language called Bioclipse Scripting Language
(BSL), which can be used for invoking functionality or to automate complex
tasks~\cite{Bioclipse2}. Bioclipse in turn acts as base for other software
such as for example Brunn~\cite{Brunn}, which is a laboratory information
system for microplate based high-throughput screening. In this manner open
source projects empower other open source projects.

Avogadro is a 3D molecular editor and viewer aimed at preparing
and analysing computational chemistry calculations. An interesting
aspect of both Avogadro and Bioclipse is that they share some developers
with the underlying toolkits and this has driven the development of new
features in the CDK and Open Babel.
